Ensuring Fairness with Transparent Auditing of Quantitative Bias in AI Systems\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-04-25 abstract.tex
Added author
Word change

\author{\IEEEauthorblockN{1\textsuperscript{st} Chih-cheng Rex Yuan}
\IEEEauthorblockA{\textit{Institute of Information Science} \\
\textit{Academia Sinica}\\
Taipei, Taiwan \\
hello@rexyuan.com}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Bow-yaw Wang}
\IEEEauthorblockA{\textit{Institute of Information Science} \\
\textit{Academia Sinica}\\
Taipei, Taiwan \\
bywang@iis.sinica.edu.tw}
}

@@

In addition to equalized odds, there are a number of fairness measures for AI systems. Our framework aims to help third parties understand these metrics and navigate complex datasets with ease, pinpointing instances of bias and discrimination.

>>>>

\author{\IEEEauthorblockN{1\textsuperscript{st} Chih-Cheng Rex Yuan}
\IEEEauthorblockA{\textit{Institute of Information Science} \\
\textit{Academia Sinica}\\
Taipei, Taiwan \\
hello@rexyuan.com}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Bow-Yaw Wang}
\IEEEauthorblockA{\textit{Institute of Information Science} \\
\textit{Academia Sinica}\\
Taipei, Taiwan \\
bywang@iis.sinica.edu.tw}
}

@@

In addition to equalized odds, there are a number of fairness measures for AI systems. Our framework aims to help third parties apply these metrics and navigate complex datasets with ease, pinpointing instances of bias and discrimination.
